Chi-squared test example using `nycflights13` `flights` data

### 2018-09-03 inst/doc/chisq_test.Rmd

```{r}
chisq_null_distn %>% 
  p_value(obs_stat = obs_chisq, direction = "greater")
```

@@

```{r eval=FALSE}
fli_small %>%
  specify(origin ~ season) %>%  %>% # alt: response = origin, explanatory = season
  hypothesize(null = "independence") %>%
  generate(reps = 1000, type = "permute") %>%
  calculate(stat = "Chisq") %>% 
  visualize(method = "both", obs_stat = obs_chisq, direction = "right")
```

>>>>

```{r}
chisq_null_distn %>% 
  get_p_value(obs_stat = obs_chisq, direction = "greater")
```

@@

```{r eval=FALSE}
fli_small %>%
  specify(origin ~ season) %>% # alt: response = origin, explanatory = season
  hypothesize(null = "independence") %>%
  generate(reps = 1000, type = "permute") %>%
  calculate(stat = "Chisq") %>% 
  visualize(method = "both", obs_stat = obs_chisq, direction = "right")
```
